---
title: "Exploratory analysis report"
author: "Gustavo Paterno"
date: "10/29/2019"
output:
  html_document:
    toc: true
    number_sections: true
    df_print: kable
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Load packages

You can find below, the packages used in this report. 

```{r packages, message = FALSE}
# Load packages
library(tidyverse)
library(cowplot)
library(here)
```

# Load data

TO load data in Rmarkdown files you must place .Rmd file in the same folder of 
the data. As an alternative, you can use the R package [here](https://github.com/jennybc/here_here) to load data from any folder in your project (see code below).

See the package website for details and tutorials: [here](https://github.com/jennybc/here_here). 

```{r load}
# Get the correct path for the data file with the package here
path <- here("data", "processed", "processed_anura_call_data.csv")
# Load data 
d <- read.csv(path)
```

# Check if data was loaded correctly

```{r}
str(d)
head(d)
```


# Descriptive statistics of study variables

```{r}
# Calculate mean, sd, minimum and max for each study variable 
var_stats <-
  data.frame(
  var = c("Dominant Frequency", "Snout-vent length"),
  avg      = round(c(mean(d$freq), mean(d$size)), digits = 1),
  sd       = round(c(sd(d$freq), sd(d$size)), digits = 1),
  min      = c(min(d$freq), min(d$size)),
  max      = c(max(d$freq), max(d$size))
)

var_stats

```


# Distribution of numeric variables

You can find below the distribution of each study variables in log and untransformed scale.

```{r plots, message = FALSE}
# Plot parameters
base_size = 12

# 2.1 Dominant frequency------
g1 <-
  ggplot(d, aes(x = freq)) +
  geom_histogram(fill = "steelblue", color = "white") +
  theme_classic(base_size = base_size) +
  labs(x = "Dominant frequency (hertz)",
       y = "Number of species")

# 2.2 Dominant frequency (log)------
g2 <-
  ggplot(d, aes(x = freq)) +
  geom_histogram(fill = "steelblue", color = "white") +
  scale_x_continuous(trans = "log10") +
  theme_classic(base_size = base_size) +
  labs(x = "Dominant frequency (hertz)[log10]",
       y = "Number of species")

# 3.1 Body size------
g3 <-
  ggplot(d, aes(x = size)) +
  geom_histogram(fill = "darkgreen", color = "white", alpha = .7) +
  theme_classic(base_size = base_size) +
  labs(x = "Snout-vent length (mm)",
       y = "Number of species")

# 3.2 Dominant frequency (log)------
g4 <-
  ggplot(d, aes(x = size)) +
  geom_histogram(fill = "darkgreen", color = "white", alpha = .7) +
  scale_x_continuous(trans = "log10") +
  theme_classic(base_size = base_size) +
  labs(x = "Snout-vent length (mm)[log10]",
       y = "Number of species")

# 4. All figures togther-----
# align vertical and horizontal axis
# Align by the lefth margin (axis = "l")
gall <- plot_grid(g1, g2, g3, g4, labels = c("A", "B", "C", "D"), 
                  align = "hv", axis = "l")
gall
```
